Ecological Modeling HW5

### 2018-04-22 1062_class/eco_model/HW/C6/HW5.rmd
up

#### Plotting
```{r dpi=1000, out.width="70%", out.height="70%"}
library(ggplot2)
library(latex2exp)
ggplot(bifurcation, aes(x=r, y=N))+
    geom_point(size = 0.01, color="#F8766D", alpha = 0.23)+
    scale_x_continuous(breaks = seq(1,5,0.5))+
    scale_y_continuous(breaks = 0:8)+
    labs(title=TeX("N_{t + 1} = N_t e^{r (1-N_t)}"),
         y=TeX("N_t"))
```

>>>>

#### Plotting
```{r dpi=700, out.width="70%", out.height="70%"}
library(ggplot2)
library(latex2exp)
ggplot(bifurcation, aes(x=r, y=N))+
    geom_point(size = 0.01, color="#F8766D", alpha = 0.23)+
    scale_x_continuous(breaks = seq(1,5,0.5))+
    scale_y_continuous(breaks = 0:8)+
    labs(title=TeX("N_{t + 1} = N_t e^{r (1-N_t)}"),
         y=TeX("N_t"))
```
